---
title: "Lab7Markdown"
author: "Anna PerezWelter"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hi Sandy!

Are you going to Scarborough Fair? Parsely, sage, rosemary and thymeeeeee

```{r}
# Load required packages
library(tidyverse)

# Read data set
kermit <- read_csv("kermit.csv")

# Was there a significant difference in kermit perception pre and post talk
# Make kermit histogram
kermit_hist <- ggplot(kermit, aes(x = Score.pre))+
  geom_histogram()+
  facet_wrap(~ Gender)

kermit_hist
```

Creator: Rank-based tests. 

Perform Ranked-Based Tests on Kermit DataFrame

Is there a significant difference in pre-talk kermit scores for males and females? 

Levels are in column called gender

Unpaired data: Mann-Whitney U
(same code as Wilcox.test function -> would use wilcox if data is paired)
Male vs Female is not paired; ranks are paired
Data frame that using should be most recent -> use data = . since the function was developed prior to piping 
```{r}

#Is there a significant difference in pre-talk Kermit scores for males and females?

#Unpaired Data: Mann-Whitney U

mwu_kermit <- kermit %>%
  wilcox.test(Score.pre ~ Gender, data = .)
mwu_kermit
```

Is there a significant difference in Kermit ranks for pre-talk and post-talk scores (ignoring all other varibles)?

Perform two-tailed test


H0: There is no significant difference in Kermit ranks for pre and post talk scores
HA: There is significant difference in Kermit ranks for pre and post talk scores

```{r}
# Use wilcox test because this is PAIRED -> since it is pre and post rank it is paired

wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)
wsr_kermit

# Retain the null. There is no significant difference in kermit rankings before and after his talk (include statistical summary)
```

